A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-27 tex/paper.tex
works with multiple orders

\item Repeat this procedure with different initializations (Step 1), to ensure that a global 
maximum in the posterior probability distribution is being sampled.
\end{enumerate}
The number of Metropolis-Hastings iterations in each step is somewhat arbitrary, and can be tuned 
for optimization purposes; we typically set $N_{MH} \approx 10$.  The number of Gibbs sampler 
iterations, $N_G$, are determined empirically with a convergence criterion .... \comm{how exactly?}

>>>>

\item Repeat this procedure with different initializations (Step 1), to ensure that a global 
maximum in the posterior probability distribution is being sampled.
\end{enumerate}
The number of Metropolis-Hastings iterations in each step is somewhat arbitrary, and can be tuned 
for optimization purposes; we typically set $N_{MH} \approx 10$.  The number of Gibbs sampler 
iterations, $N_G$, are determined empirically with the Gelman-Rubin convergence diagnostic ensuring it is below $1.1$, which compares inter-chain and intra-chain variance \citep[Eqn 11.4]{gelman13} and represents the scale by which the distribution might be reduced by continuing the simulation for infinity. Splitting chains and assessing mixing.
